A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-28 UAM2014/Article/article.tex
la2pdf commit - 2014:04:28	12:12:50	(Mon28.Apr)
Writing UA conference paper

\title{A GPU Sonar Simulator for Automatic Target Recognition}%
%
\author{J.I.Buskenes\firstAddress, \O{}ivind Midtgaard\secondAddress, Herman Midelfart\secondAddress}%
%
\begin{contact}
  \firstAddress Dept. of Informatics, P.O.Box 1080 Blindern, N-0316 OSLO
  \secondAddress Norwegian Defence Research Establishment (FFI) P.O.Box 25, NO-2027 Kjeller
\end{contact}%
%
\begin{contact}
Contact author: Jo Inge Buskenes\\
Dept. of Informatics, Univ. of Oslo, P.Box 1080 Blindern, N-0316 OSLO\\
\href{mailto:joibu@ifi.uio.no}{joibu@ifi.uio.no}
\end{contact}%
%
\begin{abstract}
Template matching is a common technique used when classifying objects in synthetic aperture sonar (SAS) images. The principle is to isolate an image segment containing an object of interest, correlate it with a set of template images, and assign it to the class of the template yielding the highest correlation coefficient. The challenge is to come up with a suitable set of template images considering that no seabed or object is truly alike.

@@

The result is a fast performing, mobile and portable on-the-fly template generator which can adapt its behavior to the nature of the current scene. We believe this can prove a powerful tool for mobile sonar imaging platforms such as autonomous underwater vehicles (AUVs).
\end{abstract}%
%
\keywords{Adaptive beamforming, minimum variance, MVDR, LCA, complexity, sonar}

@@

>>>>

\title{A GPU Sonar Simulator for Automatic Target Recognition}%
%
\author{Jo Inge Buskenes\firstAddress, \O{}ivind Midtgaard\secondAddress, Herman Midelfart\secondAddress}%
%
\begin{contact}
  \firstAddress Dept. of Informatics, P.O.Box 1080 Blindern, N-0316 OSLO\\
  \secondAddress Norwegian Defence Research Establishment (FFI) P.O.Box 25, NO-2027 Kjeller
\end{contact}%
%
\begin{contact}
Contact author: Jo Inge Buskenes\\
Dept. of Informatics, Univ. of Oslo, P.Box 1080 Blindern, N-0316 OSLO\\
\href{mailto:joibu@ifi.uio.no}{joibu@ifi.uio.no}
\end{contact}%
%
\begin{abstract}
Template matching is a common technique used when classifying objects in synthetic aperture sonar (SAS) images. The principle is to isolate an image segment containing an object of interest, correlate it with a set of template images, and assign it to the class of the template yielding the highest correlation coefficient. The challenge is to come up with a suitable set of template images considering that no seabed or object is truly alike.

@@

The result is a fast performing, mobile and portable on-the-fly template generator which can adapt its behavior to the nature of the current scene. We believe this can prove a powerful tool for mobile sonar imaging platforms such as autonomous underwater vehicles (AUVs).
\end{abstract}%
%
\keywords{Sonar, SAS, simulator, template, OpenGL}

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{data_sylinder}%
\end{subfigure}
\end{figure}

\begin{figure}[tp]\centering%
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged.svg}%
\caption{``Typical'' parameters: Length 2.6\;m, burial depth 0.1\;m, aspect angle 100$^\circ$. }%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\caption{Parameters adapted to fit SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.}%
\end{subfigure}
\caption{Cylinder simulations}\label{sim_cylinder}
\end{figure}
